---
title: "Code Portfolio - Week11"
author: "HTakano"
date: "5/29/2019"
output: html_document
---

## Hierarchical Clustering
```{r, message=FALSE, warning=FALSE}
library(tidyverse)  
library(cluster)    
library(factoextra) 
library(dendextend)
```

### hclust
``hclust()`` implements hierarchical clustering. Suitable for Agglomerative Hierarchical Clustering. Below is an example of hierarchical clustering of the data US Arrest, with agglomeration method = manhattan and hc method = average.

```{r, message=FALSE, warning=FALSE}
ft <- gmNA3
ft1 <- gmNA3$
df11 <- scale(df01)
head(df11)
```
```{r, message=FALSE, warning=FALSE}
immidataNoNA <- na.omit(gmNA3)
immidataNoNA2 <- as.numeric(select(immidataNoNA, -life, -income))
df11 <- scale(immidataNoNA2)
```



d11 <- dist(df11, method = "manhattan")
hc11 <- hclust(d11, method = "average" )
plot(hc11, cex = 0.7, hang = -1)
```

### agnes
``agnes()`` works similar to ``hclust()``, but it also can gives us the agglomerative coefficient.

```{r, message=FALSE, warning=FALSE}
library(cluster)
hc112 <- agnes(df11, method = "average")
hc112$ac
```
* This agglomerative coefficient is the measurement of the amount of clustering structure found.

* Let's check how Ward’s method identifies the strongest clustering structure of the four methods assessed as the following.

```{r, message=FALSE, warning=FALSE}
library(purrr)
Ward11 <- c( "average", "single", "complete", "ward")
names(Ward11) <- c( "average", "single", "complete", "ward")
acAll <- function(x) {
  agnes(df11, method = x)$ac
}
map_dbl(Ward11, acAll)
```

```{r, message=FALSE, warning=FALSE}
hc113 <- agnes(df11, method = "ward")
pltree(hc113, cex = 0.7, hang = -1, main = "Agnes Dendrogram") 
```


### diana
``diana()`` computes a divisive hierarchical clustering of the data set returning an object of class. Suitable for Divisive Hierarchical Clustering. It can tell us the divise coefficient as well.

```{r, message=FALSE, warning=FALSE}
hc114 <- diana(df11)
hc114$dc
pltree(hc114, cex = 0.7, hang = -1, main = "Diana Dendrogram")
```

### With Dendrogram (Ward's method)

```{r, message=FALSE, warning=FALSE}
hc115 <- hclust(d11, method = "ward.D2" )
sg11 <- cutree(hc115, k = 4)
table(sg11)
plot(hc115, cex = 0.8)
rect.hclust(hc115, k = 4, border = 2:5)
```

### fviz_cluster
``fviz_cluster()`` provides another elegant way of scatter plot.
```{r, message=FALSE, warning=FALSE}
fviz_cluster(list(data = df11, cluster = sg11))
```


### tanglegram
``tanglegram()`` plots a tangram plot of a side by side trees.
```{r, message=FALSE, warning=FALSE}
tango11 <- dist(df11, method = "manhattan")
thc11 <- hclust(tango11, method = "average")
thc112 <- hclust(tango11, method = "ward.D2")
dg11 <- as.dendrogram (thc11)
dg112 <- as.dendrogram (thc112)
tanglegram(dg11, dg112)
```

```{r, message=FALSE, warning=FALSE}
dglist11 <- dendlist(dg11, dg112)
tanglegram(dg11, dg112,
  highlight_distinct_edges = FALSE, 
  common_subtrees_color_lines = FALSE, 
  common_subtrees_color_branches = TRUE, 
  main = paste("entanglement =", round(entanglement(dglist11), 2))
  )
```


### fviz_nbclust
``fviz_nbclust()`` is used to determine optimal clustering with a couple of different methods as below.

```{r, message=FALSE, warning=FALSE}
fviz_nbclust(df11, FUN = hcut, method = "wss") # Elbow Method
fviz_nbclust(df11, FUN = hcut, method = "silhouette") # Average Silhouette Method
gap_stat11 <- clusGap(df11, FUN = hcut, nstart = 25, K.max = 10, B = 50)
fviz_gap_stat(gap_stat11)
```
