---
title: "Code Portfolio - Week3"
author: "HTakano"
date: "4/3/2019"
output: html_document
---

### "ls" 
``ls()`` function displays all the objects in the working environment. The following example demonstrates printing the resulted value of "chair1", which is 2.414214.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
ob1 <- 3.2
ob2 <- sqrt(ob1)
ob3 <- ob1 * ob2
```
```{r, message=FALSE, warning=FALSE}
ls()
ls(all.names = TRUE)
```

### "rm" 
``rm()`` function removes targeted objects from the workspace. For example, I would like to remove "ob1" from the previous workspace.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
rm(ob1)
```
```{r, message=FALSE, warning=FALSE}
ls()
ls(all.names = TRUE)
```
"ob1" was removed successfully. I sometimes use ``knitr::clean_cache()`` to clear the cache in workspace otherwise some functions do not work properly, especially for knitting to publilsh in presentation formats.

### "getwd" 
``getwd()`` function prints the current working directly. It's on my desktop and in my "506 Code Portfolilo" folder :) We can also use ``setwd()`` to change this.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
getwd()
```

### "write.tablel" & "read.table"
``write.table()`` function is used to export r data files as simple text files that also can be read with Excel, and etc. Conversely, ``setwd()`` is used to read .txt files into R. As an example below, I use a sample text data "Chart Data" to read.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
read.table("~/Desktop/506 Code Portfolio/Week3/Chart data.txt")
```
Reading files into R, ``read.csv`` and ``read.delim`` are other options for specified data files.

