---
title: "Code Portfolio - Week12"
author: "HTakano"
date: "6/7/2019"
output: html_document
---

## PCA (Principal Components Analysis)

```{r, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
wine12 <- read_csv("~/Desktop/wine.csv")
glimpse (wine12)
```

```{r, message=FALSE, warning=FALSE}
X  <- wine12[,-1]
Xscaled12 <- scale(wine12)
winePCA12 <- prcomp(Xscaled12)
summary(winePCA12)
```

```{r, message=FALSE, warning=FALSE}
Xnew12 <- winePCA12$x[,(1:5)]
head(Xnew12)
```

### princomp
``princomp()`` performs a principal components analysis on the given numeric data matrix and returns the results as an object of class ``princomp``.

```{r, message=FALSE, warning=FALSE}
pca12 <- princomp(mtcars)
screeplot(pca12)
```
```{r, message=FALSE, warning=FALSE}
library(factoextra)
var12 <- get_pca_var(pca12)
var12
```
```{r, message=FALSE, warning=FALSE}
install.packages("corrplot", repos = "http://cran.us.r-project.org")
library("corrplot")
```
```{r, message=FALSE, warning=FALSE}
library("corrplot")
corrplot(var12$coord, is.corr=FALSE)
```

### ggbiplot from Data Camp
```ggbiplot()`` lelt us draw biplot by using ggplot. I will illustrate the mtcars pca with ggbiplot.

```{r, message=FALSE, warning=FALSE}
install.packages("devtools", repos = "http://cran.us.r-project.org")
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
```

```{r, message=FALSE, warning=FALSE}
mtcars.pca <- prcomp(mtcars[,c(2:8,10,11)], center = TRUE,scale. = TRUE)
ggbiplot(mtcars.pca)
```

```{r, message=FALSE, warning=FALSE}
mtcars.pca <- prcomp(mtcars[,c(2:8,10,11)], center = TRUE,scale. = TRUE)
ggbiplot(mtcars.pca)
```


*The folowing code chunk is from Data Camp Tutorial of PCA.*
*(https://www.datacamp.com/community/tutorials/pca-analysis-r)*
*I only copied these codes to see how the ggbiplot with ellipse look like, because this is my very first time to see/use plot with ellipses like this.*
```{r, message=FALSE, warning=FALSE}
mtcars.country <- c(rep("Japan", 3), rep("US",4), rep("Europe", 7), rep("US",3), "Europe", rep("Japan", 3), rep("US",4), rep("Europe", 3), "US", rep("Europe", 3))
ggbiplot(mtcars.pca, ellipse = TRUE,  labels = rownames(mtcars), groups = mtcars.country)
```