---
title: "Code Portfolio - Week2"
author: "HTakano"
date: "3/27/2019"
output: html_document
---

### "readr" 
``readr()`` function let us read files fast. The following example demonstrates reading the data set EPA2017 file in csv format smoothly. As this week’s example data, I use US EPA 2017 data, named “EPA2017”.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
library(readr)
EPA2017 <- read_csv("~/Desktop/EPA2017.csv")
print(EPA2017)
```

### “nrow” & “ncol”
``nrow()`` function tells us how many rows in the data set and ``ncol()`` tells us how many columns in a data set. The example below shows the number of rows and columns in the data set EPA2017.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
nrow(EPA2017)
ncol(EPA2017)
```

### “str”
``str()`` function displays the internal structure of a data set. I found this as one of the most useful functions to idenfify data sets. As below, str(EPA2017) shows important information about the data set such as number of observations/variables, and class types.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
str(EPA2017)
```

### “head” & “tail”
``head()`` function displays the first several rows of a data set, while ``tail()`` function displays the last several rows of a data set. As an example, I would like to find out the first & last 6 rows of 1-5 of 7 columns.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
head(EPA2017[, c(7:12, 6)])
tail(EPA2017[, c(7:12, 6)])
```

### “filter”
``filter()`` fuction allows us to find rows/cases where conditions are true. I found this to be useful when I only want to see specific observations that satisfy specified conditions. Below, I am trying to see the number of entry with POC level = 2. It looks lilke there are 6350 entries with POC=2.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
library(dplyr)
filter(EPA2017, `POC` == 2) 
```

### “summary”
``summary()`` function returns the values of a data set or targeted variable and results of various modell fitting fuctions, such as mean, median, minimum, maximum, 1st & 3rd quantiles. The following example shows the summary of the entire EPA2017 data set.

#### *Example:*
```{r, message=FALSE, warning=FALSE}
summary(EPA2017)
```
