---
title: "Code Portfolio - Week4"
author: "HTakano"
date: "4/10/2019"
output: html_document
---

#### *- Fundamentals of R markdown -*
#### *- Exploring with other languages -*

### Code Chunks

R markdown code chunks are written as
```{r}
```
The "{r}" part can be modified for suitable knit output options. Most common options are displayed as the following code chunk.
```{r, echo=TRUE, eval=TRUE, message=TRUE, warning=TRUE}
x4 <- 2 + 3
```

### Inline Code

Inline codes are written as `r `. I am trying to insert the result of as inline code below.

```{r, message=FALSE, warning=FALSE}
bird4 <- 10^6
```
> `r bird4` ounce = 62500 pound


### Python 

In order to use Python code in R properly, I needed to install ``"reticulate"`` package with the CRAN url.

```{r, message=FALSE, warning=FALSE}
install.packages("reticulate", repos = "http://cran.us.r-project.org")
```
```{r}
library(reticulate)
use_python("/usr/local/bin/python")
```
```{python}
x = 'OMG, Python in R!'
print(x.split(' '))
```
Another example of python chunk with plot.
```{python}
import matplotlib.pyplot as plt
plt.plot([3, 12, 0, 4])
plt.show()
```

### Bash

```{bash}
ls *Rmd
```


### Parameters
R markdown documents can include one or more parameters whose values can be set for rendered reports. 
The following example is the sea ice data that I used for another project. I have set the parameters as; month = August, pole = North pole, and the year = 1979 with customized color fill.

```{r, warning=FALSE, message=FALSE}
library(rnoaa)
library(rgdal)
library(ggplot2)
```
```{r, warning=FALSE, message=FALSE}
urls <- seaiceeurls(mo = 'Aug', pole = 'N', yr = 1979)
out <- seaice(urls)
ggplot(out, aes(long, lat, group = group)) + 
  geom_polygon(fill = "skyblue1") + 
  theme_ice()
```

### Tables and kable

R automatically displays data frames and matrixes as defults, but it can be shown with additional formatting.
```{r, message=FALSE, warning=FALSE}
library(knitr)
kable(iris[5:12, ], caption = "Iris knitr kable")
```

### Basics

R markdown text can be formatted as other word documents.

> # Header 1
> ## Header 2
> ### Header 3
> #### Header 4
> ##### Header 5

1. first
2. second
3. third

- *italics*
- **bold**
- `monospace`
- [hyperlink to Google](google.com)
- Equation $e^{i\pi} + 1 = 0$

### Output Formats
R markdown documents can be rendered to other formats such as MS Word. I will try demonstrating it with 

```{r, warning=FALSE, message=FALSE}
library(rmarkdown)
library(viridis)
```
```{r, warning=FALSE, message=FALSE}
image(volcano, col = viridis(670, option = "B"))
```

============================================