---
title: "Code Portfolio - Week6"
author: "HTakano"
date: "4/25/2019"
output:
  html_document: default
---

### filter
``filter()`` allows us to subset observations based on their values. As an example, I filtered the iris data by Petal.Length=1.5.
```{r, message=FALSE, warning=FALSE}
library(dplyr)
data(iris)
filter(iris, Petal.Length == 1.5)
```

### arrange

``arrange()`` function is similar to ``filter()``, however, it changes their order instead of selecting rows. I am trying to arrnage the iris data by the descending order of Sepal.Width.
``arrange()`` function is similar to ``filter()``, however, it changes their order instead of selecting rows. As a
```{r, message=FALSE, warning=FALSE}
arrange(iris, desc(Sepal.Width))
```

### mutate
``mutate()`` allows us to add or transform columns as below.
```{r, message=FALSE, warning=FALSE}
mutate(iris, Sepal.Length - Petal.Length)
```
```{r, message=FALSE, warning=FALSE}
transmute(iris, Sepal.Length - Petal.Length)
```

### mean
``mean()`` function computes the mean of argument(). Below, I will find out the mean of Petal.Length of iris data.
```{r, message=FALSE, warning=FALSE}
mean(iris$Petal.Length)
```

### median
``median()`` function coputes the median of the argument(). I will use the same variable to compare the mean, median, weighted mean, and weighted median.
```{r, message=FALSE, warning=FALSE}
median(iris$Petal.Length)
```

### weightedmean
With ``raster`` package, ``weightedmean()`` function computes the weighted mean of the argument (). 
```{r, message=FALSE, warning=FALSE}
library(raster)
weighted.mean(iris$Petal.Length)
```

### weightedmedian
``weightedMedian()`` computes the weighted median of the argument() with ``matrixStats`` package as follows.
```{r, message=FALSE, warning=FALSE}
library(matrixStats)
weightedMedian(iris$Petal.Length)
```


